On Secure Delegation of SampBQP with a Classical Client

### 2020-03-19 qpip.tex
Fix typos

In this section, we construct a one-message $\QPIP_1$ delegation protocol for $\SampBQP$.
At a high level, it is a cut-and-choose protocol.
The server constructs multiple copies of the ground state as certificates,
then the client randomly chooses a copy to output and checks the rest.
Unfortunately we have inverse polynomial soundness errors here.

@@

The other challenge is that a cheating prover's certificates can be arbitrarily entangled,
so common techniques such as Chernoff bounds can't be applied as-is.
This wasn't a challenge for $\Piblind$ for $\BQP$ earlier because its soundness is one-sided:
we only guarantee that a client cannot accept a no-instance;
a cheating server is allowed to cause the client to reject a yes-instance.
Because of this asymmetry, a cheating prover's for $\Piblind$ optimal strategy is to maximize its acceptance probability,
which corresponds to sending $n$ identical copies of some state.
In our case with $\SampBQP$, we overcome this challenge by using de Finetti's theorem
to approximate our measurement results with that of measurement results on some unentangled copies.

@@

	Pick $\varepsilon$ small enough so it holds for all $\phi$ that:
	\begin{equation}
		\label{QPIP1eps}
		P[\cA_\GS(\phi)=acc]>\frac{1}{2}-2\varepsilon\Rightarrow\braket{\phi|H_{C'(x)}|\phi}<\frac{1}{T^\lambda}
	\end{equation}

@@

	\begin{enumerate}
		\item The verifier privately samples $I\subset[N]$ s.t. $\abs{I}=n$, and $k\xleftarrow{\$}[N]\setminus I$.
		\item The honest prover prepares $N$ copies of $\ket{\psi_{C'(x)}}$ and sends all of it to the verifier qubit-by-qubit.
		\item For $i$ from $1$ to $N$, the verifier chooses what to do to $\rho_i$ as follows:
		\begin{enumerate}
			\item If $i\in I$, run $\cA_{\GS}(\rho_i)$.
			\item Otherwise, if $i=k$, measure the data register of $\rho_i$ and save the outcome as $y$.
			\item Otherwise, discard $\rho_i$.
		\end{enumerate}
		\item If the proportion of copies accepted by $\cA_{\GS}$ is greater than $\frac{1}{2}-\varepsilon$ then the verifier accepts and outputs $y$. Otherwise, it rejects.
	\end{enumerate}
\end{protocol}

@@

	For $i\notin I$ we have
	$$\sum_{i\in I} w_i p_i<2^{-\lambda}=\negl(\lambda)$$

	For $i\in I$ we have
	$$P[\cA_\GS(\rho_i)=acc]>\frac{1}{2}-2\varepsilon$$
	and hence
	$$\braket{\rho_i|H_{C'(x)}|\rho_i}<\frac{1}{T^\lambda}$$
	by \cref{QPIP1eps}.
	We also know that the least nonzero eigenvalue of $H_{C'(x)}$ is lower-bounded by $\frac{3}{4}$, so we obtain \Ethan{at least I think we do. Need theorem.}
	$$\braket{\rho_i|\phi_{C'(x)}}>1-O(T^{-\lambda})$$
	\Ethan{Now we need some kinda standard fidelity argument to show that the measurement results will be close too. I'm not familiar with them at the moment.}

>>>>

In this section, we construct a one-message $\QPIP_1$ delegation protocol for $\SampBQP$.
At a high level, it is a cut-and-choose protocol.
The server constructs multiple copies of the ground state as certificates,
then the client randomly chooses a copy to output and checks the rest.
Unfortunately our approach incurs inverse polynomial soundness errors.

@@

The other challenge is that a cheating prover's certificates can be arbitrarily entangled,
so common techniques such as Chernoff bounds can't be applied as-is.
This wasn't a challenge for $\Piblind$ for $\BQP$ earlier because...
\Ethan{TODO; need brief and intuitive explanation}
In our case with $\SampBQP$, we overcome this challenge instead by using de Finetti's theorem
to approximate our measurement results with that of some unentangled copies,
within inverse polynomial errors.

@@

	Pick $\varepsilon$ small enough so it holds for all $\ket\phi$ that:
	\begin{equation}
		\label{QPIP1eps}
		P[\cA_\GS(\ket{\phi})=acc]>\frac{1}{2}-2\varepsilon\Rightarrow\braket{\phi|H_{C'(x)}|\phi}<\frac{1}{T^\lambda}
	\end{equation}

@@

	\begin{enumerate}
		\item The verifier privately samples $I\subset[N]$ s.t. $\abs{I}=n$.
			It then privately samples $k\xleftarrow{\$}[N]\setminus I$.
		\item The honest prover prepares $N$ copies of $\ket{\psi_{C'(x)}}$ and sends all of them to the verifier qubit-by-qubit.
		\item For $i$ from $1$ to $N$, the verifier chooses what to do to the $i$-th copy, $\rho_i$, as follows:
		\begin{enumerate}
			\item If $i\in I$, run $\cA_{\GS}(\rho_i)$.
			\item Otherwise, if $i=k$, measure the data register of $\rho_i$ and save the outcome as $y$.
			\item Otherwise, discard $\rho_i$.
		\end{enumerate}
		\item If the proportion of copies accepted by $\cA_{\GS}$ is greater than $\frac{1}{2}-\varepsilon$ then the verifier accepts and outputs $y$. Otherwise, it rejects.
	\end{enumerate}
\end{protocol}

@@

	For $i\notin I$ we have
	$$\sum_{i\in I} w_i p_i<2^{-\lambda}=\negl(\lambda)$$
	so we can approximate with negligible error that all $\rho_i$ where $i\notin I$ are rejected.

	For $i\in I$ we have
	$$P[\cA_\GS(\rho_i)=acc]>\frac{1}{2}-2\varepsilon$$
	and hence
	$$\braket{\rho_i|H_{C'(x)}|\rho_i}<\frac{1}{T^\lambda}$$
	by \cref{QPIP1eps}.
	We also know that the least nonzero eigenvalue of $H_{C'(x)}$ is lower-bounded by $\frac{3}{4}$, so we obtain... \Ethan{TODO not done yet. Probably some squares or square roots missing here.}
	$$\braket{\rho_i|\phi_{C'(x)}}>1-O(T^{-\lambda})$$
	\Ethan{Now we need some kinda standard fidelity argument to show that the measurement results will be close to as if the ground state is measured.}
